Security Audit of Safeplug ``Tor in a Box''

### 2014-02-26 w2sp/report.tex
figures
changes from email
more edits, added legality paragraph about tor relays/exits

% *** SUBFIGURE PACKAGES ***
%\usepackage[tight,footnotesize,caption=false]{subfig}
\usepackage[caption=false]{subfig}
% subfigure.sty was written by Steven Douglas Cochran. This package makes it
% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
% work, it is a good idea to load it with the tight package option to reduce
% the amount of white space around the subfigures. subfigure.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at:
% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
% subfigure.sty has been superceeded by subfig.sty.
% subfig.sty, also written by Steven Douglas Cochran, is the modern
% replacement for subfigure.sty. However, subfig.sty requires and
% automatically loads Axel Sommerfeldt's caption.sty which will override
% IEEEtran.cls handling of captions and this will result in nonIEEE style
% figure/table captions. To prevent this problem, be sure and preload
% caption.sty with its "caption=false" package option. This is will preserve
% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later 
% (recommended due to many improvements over 1.2) of subfig.sty supports
% the caption=false option directly:
%\usepackage[caption=false,font=footnotesize]{subfig}
%
% The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
% The latest version and documentation of caption.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/

@@

\begin{abstract}
%\boldmath
We present the first public third-party security audit of Pogoplug's Safeplug device, which marketed ``complete security and anonymity online'' by using Tor technology to protect users' IP addresses.  We examine the hardware, software, and network behavior of the Safeplug device, as well as the user experience in comparison to other forms of web browsing.  Although the Safeplug appears to use Tor as advertised, users may still be identified in ways they may not expect.  Furthermore, an engineering vulnerability in the Safeplug's settings commands would allow an adversary internal or external to a user's home network to silently disable Tor or modify other Safeplug settings, which completely overrules the security claims of the device.  Even if the engineering problem is fixed, the user experience challenges of this type of device make it inferior to the existing standard in anonymity methods, the Tor Browser Bundle.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

@@

The cloud storage company Pogoplug noticed the demand for online anonymity and in November of 2013 they released the Safeplug.  This device is a small box that plugs into a user's home router and by routing all traffic through Tor, it claims to: conceal your identity, hide where you live, shield your surfing habits, and make you anonymous online~\cite{pogo}.  The Safeplug also claimed simple setup and an abstraction of any technical detail, as shown by the setup instructions that came with the device shown in Figure~\ref{fig:instructions}.  A device such as this should be audited to confirm or deny the validity of the bold security claims.  We conducted the first public third-party security audit of the Safeplug by analyzing the hardware, software, and network behavior.  The following are some of our findings:

@@

\begin{figure*}
\centering
\includegraphics[width=.6\textwidth]{safeplug_flowchart}
\caption{Flowchart demonstrating the actual functionality of the Safeplug as an HTTP proxy between a device's browser and the home network's router.}
\label{fig:flow}
\end{figure*}

@@

{\bf Safeplug.} Safeplug is a product that launched in December of 2013 from the cloud storage company Pogoplug, that offers any user the option of using Tor without having to know about it or how it works.  It allows users to browse the web from their own standard web browser with “complete security and anonymity” for the cheap price of \$49 \cite{safeplug}.  Safeplug offers Tor out of the box, with no additional software installation, by sitting between a user's router and the internet \cite{wired}.  Pogoplug's marketing pitch centers around the protection of users' IP addresses by using Tor \cite{safeplug,bittech}.

@@

Following good security and development practices, the Safeplug makes use of several pieces of Open Source software.  A standard term of many open source licenses states that a company that uses the open source software must list the software used and its license, as well as the open source code of their own software that uses the license.  The TOS conatins a link to a page that woudl supposedly comply with this requirement  \url{http://pogoplug.com/home-en-developers-open-source.html}\cite{safeplug} but the link is dead and instead the reader sees a 404 error.  This dead link was noted by some members of the Tor-talk mailing list in November 2013\cite{tormailinglist} and has not been fixed as of Feburary 2014.  Pogoplug's open source page does exist at \url{https://pogoplug.com/opensource} and includes several pieces of software for the Safeplug: bootloader, Linux kernel, XCE kernel support driver, glibc, BusyBox, and a Safeplug source bundle.  However, there is no way to find this page from the Terms of Service.

The final area of interest was software updates on the device which will be ``automatically delivered'' to the user, but it is unclear whether there will be any notification~\cite{safeplug}.  Although a prompt updating mechanism is an important security feature for users who trust Pogoplug and their update servers (in fact the activation process seems designed for keeping the software up to date and it is concerning that this does not seem to uniformly occur as discussed in Section~\ref{versions}), other users might want to disable this functionality for fear of a malicious use of Pogoplug's servers or a spoofing attack (see Section \ref{dnsspoof} for more details of this attack).  This is one of the many reasons why users who truly need security and anonymity should opt for the Tor Browser Bundle rather than adding the Safeplug to their network.

@@

The link provided is to an advertisement-filled and not particularly reputable looking website with no clear navigation to get to the necessary instructions.

If the majority of users can only understand the simpler description, then they likely won't understand the description of a Tor relay node.  This could be a problem if users simply decide not to do anything with that setting (i.e. don't change the setting to use Safeplug as a relay node).  In this case, there would be a large increase in use of the Tor network, yet most of the users are not giving back to it.

@@

\subsection{Hardware}
Before investigating the software, we took apart one of the two Safeplug devices we purchased in order to see the physical components.  Figure~\ref{fig:top} shows the top of the board and Figure~\ref{fig:bottom} shows the bottom.  The board incorporates: (A) an SD card slot, (B) a power connector, (C) a USB slot, (D) an ethernet connector, (E) ethernet transceiver, (F) lan transformer, (G) the Marvell 88F6192 integrated controller, and (H), (I) flash memory.  The Marvell controller is from 2008 and runs ARM~\cite{marvellhw}. This is the same controller as version 4 of Pogoplug's cloud storage device - and takedowns of that device available online show an identical-looking circuit-board to the one in Figure~\ref{fig:circuit}\cite{pogo4}.  Also of note: the Safeplug branding is a sticker on the front of the device, whereas the Pogoplug branding is etched into the plastic on top of the device, which indicates that the Safeplug uses the same hardware as Pogoplug's existing devices, and derives its differing functionality from different software.

@@

The Safeplug runs version 2.6.31.8 of Arch Linux on an ARM architecture, which was produced at the end of 2009 and installed on 23 August 2011.  Unsurprising for its age, there are a number of network vulnerabilities for this version of the kernel - most of which produce denial of service attacks if an adversary sends a particularly formed packet \cite{kernelcve}.  This is the same version of Linux that runs on Version 4 of PogoPlug's Mobile platform \cite{archforum}.

The software installed by the activation process on the Safeplug is in \verb!/opt/xce! and includes lighttpd, privoxy, and tor.  Lighttpd is an open-source webserver, which is serving the settings page on the device - the project's description mentions ``security, speed, compliance, and flexibility [... while being] designed and optimized for high perfomance environments'' \cite{lighttpd}.  The version of lighttpd on the box is only one version away from being up to date, 1.4.33 which was released on 27 September 2013.  The current version of lighttpd, which has a number of security fixes, was released on 20 January 2014, after the Safeplug was purchased.  However, checking for an update from the Safeplug does not lead to any updated software installation.

@@

\subsection{Networking}
The lighttpd, Privoxy, and Dropbear software give some indication of the networking services on the device.  We used \texttt{nmap} to scan the ports.  Before the activation of the Safeplug, only ports 80 and port 3333 are open.  After the activation, without the use of Tor turned on, ports 22 for SSH, port 80 for settings access and port 8080 for http-proxy are open.  When Tor is turned on as a relay, port 9001 tor-orport is opened as well.  This corresponds with the note on the settings page about Tor relays discussed in Section \ref{port9001} above.

\subsection{Configuration on the Safeplug}
\label{spconfig}
The Safeplug configuration files can be found in \verb!/opt/xce/etc! and include \verb!sp.conf! and \verb!sp_version! and \verb!sp_torexceptions!.  The first contains all of the configuration details: whether to use Tor, whether to adblock, and whether to be a relay or an exit relay. The version file is used during the check for updates, and the exceptions file is used by the privoxy configuation to control the whitelist of sites not to connect to via Tor.

These configuration files are read by the scripts in \verb!/opt/xce/etc/init.d! which enable lighttpd, privoxy, and tor.  As expected, Privoxy looks at the Tor, adblock and exceptions configurations, and Tor reads the \verb!sp.conf! file to set which Tor configuration file (regular, relay or exit relay) to use.

@@

After we finished our configuration, we were taken to the Safeplug settings page.  This page is shown in Figure~\ref{fig:settings}.  This allowed us to turn Tor on/off, add white-listed websites, turn ad-blocking on/off, and turn the ability of our device to be a relay node on/off (and if on, an additional option appeared to allow the device to be an exit node.

@@

Next, we wanted to see how usable this would be to a normal Internet user.  A user would probably decide not to use Safeplug if they could not read their web pages (if they were not in their native language), or if they could not log into their accounts (some web sites will lock a user out if they try to log in from multiple countries in a short time period).  While browsing the Internet, we experienced some pages in German and Swedish, which is expected with Tor; if a user is not familiar with Tor, they may just get frustrated and stop using Safeplug altogether.  We were also prompted with a request to ``Enter the name of the city where you usually sign in'' when we tried to log into our Google account, indicating that Google noticed we were trying to login from significantly ``unusual'' location.

@@

More interesting and damaging to the user's control over their anonymity would be third-party cookies because the user cannot remove those just by logging out.  It requires a trip to the browser settings to clear cookies (or not have them set in the first place).  We used FourthParty to analyze the client's use of the Safeplug \cite{fourthparty}.  When collecting data on the existence of third-party cookies, we analyzed two separate browsing sessions; they were both new sessions with no cookies.  One of the sessions used the ad-block feature of the Safeplug and the other did not.  After analyzing data from Fourthparty, we found many third-party cookies in both sessions.  These included cookies from: abmr.net, bizographics.com, krxd.net, and bluekai.com among many others.  The adblock functionality on the Safeplug reduced but did not eliminate these third-party cookies.

Although Safeplug has a warning about clearing cookies on their FAQ page, it only mentions clearing cookies after a browser session.  Of greater concern would be tracking a user during their browser session from website to website; preventing this requires knowledge and constant viligance from the user, or a browser that does not accept third-party cookies, such as the one provided in the Tor Browser Bundle.

\subsection{Browser Fingerprinting}
We used Panopticlick~\cite{panopticlick} to examine the fingerprint of a freshly installed Firefox browser running through the Safeplug proxy.  Panopticlick found the browser to be unique.  Fingerprinting is another way in which websites could correlate and de-anonymize user traffic without knowing the IP address.

@@

\section{Implementing Attacks}
As we discovered during the software analysis, the Safeplug has a remote procedure call (RPC) capability.  This is a script called \verb!xspctrl! found in \verb!/opt/xce/html/svc! and it contains various options.  Particularly, functional calls to this script include enable and disable for all of the Safeplug settings, including Tor, ad block, and Tor relay.  None of them require any arguments in the POST string.

@@

\subsection{Insider Attack}
Since the Safeplug has no validation or authentication on the settings page or these RPC calls, an malicious party inside the network could easily modify the settings.  Such an adversary with a computer could load the Safeplug's settings page and adjust options such as disabling Tor or adding a site to the whitelist; since this page is meant to be accessible to normal internet users, anyone can perform this attack.  Unlike many home routers, there is no username/password combination necessary to access this page.

@@

Since the RPC version of the attack just involves basic internet tools (the ability to send a POST request), the attacker could also be any kind of device on the local network, or the local gateway if it is compromised.  The NSA ``Spymall'' catalog leaked in December shows tools for compromising a number of different devices and home routers are traditionally insecure \cite{spymall}.  It is easy to imagine any malicious party, not just one with the resources of a government (although governments might be some of the most interested parties in attacking a Tor proxy), compromising the gateway and using that access to make a disabling RPC call into the Safeplug.  This would occur silently from the perspective of a client unless they happen to check the Settings page for the Safeplug.  Instead, the client would continue browsing with a belief that they are protected by their use of the Tor network, while in fact any external adversary can track their traffic.

@@

The largest observed time to send requests to the 192.168.0.0/24 space was approximately 400 milliseconds; the entire attack costs approximately 800 milliseconds for sending requests to both 192.168.0.0/24 and 192.168.1.0/24 ranges - even when the website was being loaded over Tor.  In the case of a private network in the range of 172.16.0.0/16, the attack took less than ~12 minutes (this generates script timeout warnings in most major browsers, which affects the timing of this attack).  This means that it would take a few hours to send requests to the full 172.16.0.0/12 range, which is commonly used in business networks.  The final private network space is 10.0.0.0/8 which is too large for an exhaustive search, but some simple optimization might make it feasible as well.  For example, using a GET request to get and parse the Safeplug settings page would allow the script to positively identify the Safeplug and stop the search.  However, the 192.168.0.0/24 and 192.168.1.0/24 ranges are much more common in home networks; because Safeplug is geared towards home network use, in most cases the script will take less than a second, a trivial amount of time for the attacker to spend.

@@

Having a publically available root password means that SSH can be done effectively without authentication.  We tried the SSH procedure twice, once before the Internet connection and activation, and once afterwards.  Before the activation and update procedure, SSH was not available.  The simple \verb!Hbplug! software on the box could not accept this RPC call.  However, once the box was updated and had lighttpd installed, the SSH procedure was available and we could download the contents of the root filesystem for analysis.

@@

\section{Discussion}
\subsection{Engineering Fixes}
The most critical engineering fix is authentication in the POST calls to prevent the CSRF attack.  A typical example is a cookie and a hidden form field set in the Settings page of the Safeplug hosts; the cookie must be returned by the browser when making the POST request to the RPC server \cite{csrfdef}.  Although someone doing a CSRF attack such as the one described above could get the cookie sent, because of the same-origin policy, the adversary would not be able to examine the contents of the cookie to determine what to put in the form field.

@@

\subsection{Opportunities}
Despite all the structural problems, is there a market for a Torifying piece of hardware?  Given the security pitfalls in comparison to a piece of software such as the Tor Browser Bundle, there seems to be no reason for a user that can run the Tor Browser Bundle to purchase the Safeplug or any other device.  For mobile phones, the proxy problems with mobility contribute to an already high usability cost.  However, there are an emerging class of ``smart home'' devices which may connect to the internet.  It is possible that some of these devices can be configured to use an HTTP proxy or some other middle box to Torify their traffic to an external service provider.  For them, is the benefit of some anonymity via a Safeplug-like device worthwhile?  Since the data sent by these devices to the service provider likely contains identifying information, the use of Tor probably only protects the user's location at the expense of connection time and load on the Tor network.  Since proxy configuration on such devices is likely to be difficult and the amount of information hidden is unlikely to be worth the effort, a Torifying box that functions as a proxy has questionable use in this space as well.

@@

>>>>

% *** SUBFIGURE PACKAGES ***
%\usepackage[tight,footnotesize,caption=false]{subfig}
\usepackage[caption=false]{subfig}
\usepackage[center]{caption}
% subfigure.sty was written by Steven Douglas Cochran. This package makes it
% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
% work, it is a good idea to load it with the tight package option to reduce
% the amount of white space around the subfigures. subfigure.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at:
% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
% subfigure.sty has been superceeded by subfig.sty.
% subfig.sty, also written by Steven Douglas Cochran, is the modern
% replacement for subfigure.sty. However, subfig.sty requires and
% automatically loads Axel Sommerfeldt's caption.sty which will override
% IEEEtran.cls handling of captions and this will result in nonIEEE style
% figure/table captions. To prevent this problem, be sure and preload
% caption.sty with its "caption=false" package option. This is will preserve
% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later 
% (recommended due to many improvements over 1.2) of subfig.sty supports
% the caption=false option directly:
%\usepackage[caption=false,font=footnotesize]{subfig}
%
% The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
% The latest version and documentation of caption.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/

@@

\begin{abstract}
%\boldmath
We present the first public third-party security audit of Pogoplug's Safeplug device, which marketed ``complete security and anonymity online'' by using Tor technology to protect users' IP addresses.  We examine the hardware, software, and network behavior of the Safeplug device, as well as the user experience in comparison to other forms of web browsing.  Although the Safeplug appears to use Tor as advertised, users may still be identified in ways they may not expect.  Furthermore, an engineering vulnerability in the Safeplug's settings commands would allow an adversary internal or external to a user's home network to silently disable Tor or modify other Safeplug settings, which completely overrules the security claims of the device.  Even if the engineering problem is fixed, the user experience challenges of this type of device make it inferior to the existing standard in anonymity methods: the Tor Browser Bundle.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

@@

The cloud storage company Pogoplug noticed the demand for online anonymity and in December of 2013 they released the Safeplug.  This device is a small box that plugs into a user's home router and by routing all traffic through Tor, it claims to: conceal your identity, hide where you live, shield your surfing habits, and make you anonymous online~\cite{pogo}.  The Safeplug also claimed simple setup and an abstraction of any technical detail, as shown by the setup instructions that came with the device shown in Figure~\ref{fig:instructions}.  A device such as this should be audited to confirm or deny the validity of the bold security claims.  We conducted the first public third-party security audit of the Safeplug by analyzing the hardware, software, and network behavior.  The following are some of our findings:

@@

\begin{figure*}
\centering
\includegraphics[width=.4\textwidth]{safeplug_flowchart}
\caption{Flowchart demonstrating the actual functionality of the Safeplug as an HTTP proxy between a device's browser and the home network's router.}
\label{fig:flow}
\end{figure*}

@@

{\bf Safeplug.} Safeplug is a product that launched in December of 2013 from the cloud storage company Pogoplug, that offers any user the option of using Tor without having to know about it or how it works.  It allows users to browse the web from their own standard web browser with “complete security and anonymity” for the cheap price of \$49 \cite{safeplug}.  Safeplug offers Tor out of the box, with no additional software installation, by sitting between a user's router and the Internet \cite{wired}.  Pogoplug's marketing pitch centers around the protection of users' IP addresses by using Tor \cite{safeplug,bittech}.

@@

Following good security and development practices, the Safeplug makes use of several pieces of Open Source software.  A standard term of many open source licenses states that a company that uses the open source software must list the software used and its license, as well as the open source code of their own software that uses the license.  The TOS contains a link to a page that would supposedly comply with this requirement: \url{http://pogoplug.com/home-en-developers-open-source.html} but the link is dead and instead the reader sees a 404 error \cite{safeplug}.  This dead link was noted by some members of the Tor-talk mailing list in November 2013 and has not been fixed as of Feburary 2014 \cite{tormailinglist}.  Pogoplug's open source page does exist at \url{https://pogoplug.com/opensource} and includes several pieces of software for the Safeplug: bootloader, Linux kernel, XCE kernel support driver, glibc, BusyBox, and a Safeplug source bundle.  However, there is no way to find this page from the Terms of Service.

The final area of interest was software updates on the device which will be ``automatically delivered'' to the user, but it is unclear whether there will be any notification~\cite{safeplug}.  Although a prompt updating mechanism is an important security feature for users who trust Pogoplug and their update servers (in fact the activation process seems designed for keeping the software up to date and it is concerning that this does not seem to uniformly occur as discussed in Section~\ref{versions}), other users might want to disable this functionality for fear of a malicious use of Pogoplug's servers or a spoofing attack (see Section \ref{dnsspoof}).  This is one of the many reasons why users who truly need security and anonymity should opt for the Tor Browser Bundle rather than adding the Safeplug to their network.

@@

The link provided is to an advertisement-filled and not particularly reputable-looking website with no clear navigation to get to the necessary instructions.

If the majority of users can only understand the simpler description, then they likely won't understand the description of a Tor relay node.  This could be a problem if users simply decide not to do anything with that setting (i.e. don't change the setting to use the Safeplug as a relay node).  In this case, there would be a large increase in use of the Tor network, yet most of the users are not giving back to it.

@@

Another consequence of misunderstanding the use of the Safeplug as a relay node, or more specifically, as an exit node is the possible legal repercussions.  As an exit relay, all traffic that exits the node can be traced back to the Safeplug's IP address; it is likely that some of this traffic contains illegal information or is part of illegal activities.  The Tor Project recommends not running an exit relay from a user's home: ``If law enforcement becomes interested in traffic from your exit relay, it's possible that officers will seize your computer. For that reason, it's best not to run your exit relay in your home or using your home Internet connection~\cite{law}.''  Considering that the Safeplug is intended for home use, it is a poor design choice to allow the user to use it as an exit relay, especially without providing the user with any information.

\subsection{Hardware}
Before investigating the software, we took apart one of the two Safeplug devices we purchased in order to see the physical components.  Figure~\ref{fig:top} shows the top of the board and Figure~\ref{fig:bottom} shows the bottom.  The board incorporates: (A) an SD card slot, (B) a power connector, (C) a USB slot, (D) an ethernet connector, (E) ethernet transceiver, (F) lan transformer, (G) the Marvell 88F6192 integrated controller, and (H), (I) flash memory.  The Marvell controller is from 2008 and runs ARM~\cite{marvellhw}. This is the same controller as version 4 of Pogoplug's cloud storage device; takedowns of that device that are available online show an identical-looking circuit-board to the one in Figure~\ref{fig:circuit}\cite{pogo4}.  It is also interesting to note that the Safeplug branding is a sticker on the front of the device, whereas the Pogoplug branding is etched into the plastic on top of the device, which indicates that the Safeplug uses the same hardware as Pogoplug's existing devices, and derives its differing functionality from different software.

@@

The Safeplug runs version 2.6.31.8 of Arch Linux on an ARM architecture, which was produced at the end of 2009 and installed on 23 August 2011.  Unsurprising for its age, there are a number of network vulnerabilities for this version of the kernel - most of which produce denial of service attacks if an adversary sends a particularly formed packet \cite{kernelcve}.  This is the same version of Linux that runs on Version 4 of Pogoplug's Mobile platform \cite{archforum}.

The software installed by the activation process on the Safeplug is in \verb!/opt/xce! and includes Lighttpd, Privoxy, and Tor.  Lighttpd is an open-source webserver, which is serving the settings page on the device - the project's description mentions ``security, speed, compliance, and flexibility [... while being] designed and optimized for high perfomance environments'' \cite{lighttpd}.  The version of Lighttpd on the box is only one version away from being up to date, 1.4.33 which was released on 27 September 2013.  The current version of Lighttpd, which has a number of security fixes, was released on 20 January 2014, after the Safeplug was purchased.  However, checking for an update from the Safeplug does not lead to any updated software installation.

@@

[TODO: Safeplug Call Graph]

\subsection{Networking}
The Lighttpd, Privoxy, and Dropbear software give some indication of the networking services on the device.  We used \texttt{nmap} to scan the ports.  Before the activation of the Safeplug, only ports 80 and 3333 are open.  After the activation, without the use of Tor turned on, port 22 for SSH, port 80 for settings access and port 8080 for http-proxy are open.  When Tor is turned on as a relay, port 9001 tor-orport is opened as well.  This corresponds with the note on the settings page about Tor relays discussed in Section \ref{port9001} above.

\subsection{Configuration on the Safeplug}
\label{spconfig}
The Safeplug configuration files can be found in \verb!/opt/xce/etc! and include \verb!sp.conf! and \verb!sp_version! and \verb!sp_torexceptions!.  The first contains all of the configuration details: whether to use Tor, whether to ad-block, and whether to be a relay or an exit relay. The version file is used during the check for updates, and the exceptions file is used by the Privoxy configuation to control the whitelist of sites not to connect to via Tor.

These configuration files are read by the scripts in \verb!/opt/xce/etc/init.d! which enable Lighttpd, Privoxy, and Tor.  As expected, Privoxy looks at the Tor, ad-block and exceptions configurations, and Tor reads the \verb!sp.conf! file to set which Tor configuration file (regular, relay, or exit relay) to use.

@@

After we finished our configuration, we were taken to the Safeplug settings page.  This page is shown in Figure~\ref{fig:settings}.  This allowed us to turn Tor on/off, add white-listed websites, turn ad-blocking on/off, and turn the ability of our device to be a relay node on/off (and if on, an additional option appeared to allow the device to be an exit node).

@@

Next, we wanted to see how usable this would be to a normal Internet user.  A user would probably decide not to use Safeplug if they could not read their web pages (if they were not in their native language), or if they could not log into their accounts (some web sites will lock a user out if they try to log in from multiple countries in a short time period).  While browsing the Internet, we experienced some pages in German and Swedish, which is expected with Tor; if a user is not familiar with Tor, they may get frustrated and stop using Safeplug altogether.  We were also prompted with a request to ``Enter the name of the city where you usually sign in'' when we tried to log into our Google account, indicating that Google noticed we were trying to login from significantly ``unusual'' location.

@@

More interesting and damaging to the user's control over their anonymity would be third-party cookies because the user cannot remove those just by logging out.  It requires a trip to the browser settings to clear cookies (or not have them set in the first place).  We used FourthParty to analyze the client's use of the Safeplug \cite{fourthparty}.  When collecting data on the existence of third-party cookies, we analyzed two separate browsing sessions; they were both new sessions with no cookies.  One of the sessions used the ad-block feature of the Safeplug and the other did not.  After analyzing data from Fourthparty, we found many third-party cookies in both sessions.  These included cookies from: abmr.net, bizographics.com, krxd.net, and bluekai.com among many others.  The ad-block functionality on the Safeplug reduced, but did not eliminate these third-party cookies.

Although Safeplug has a warning about clearing cookies on their FAQ page, it only mentions clearing cookies after a browser session.  Of greater concern would be tracking a user during their browser session from website to website; preventing this requires knowledge and constant vigilance from the user, or a browser that does not accept third-party cookies, such as the one provided in the Tor Browser Bundle.

\subsection{Browser Fingerprinting}
We used Panopticlick to examine the fingerprint of a freshly installed Firefox browser running through the Safeplug proxy~\cite{panopticlick}.  Panopticlick found the browser to be unique.  Fingerprinting is another way in which websites could correlate and de-anonymize user traffic without knowing the IP address.

@@

\section{Implementing Attacks}
As we discovered during the software analysis, the Safeplug has a remote procedure call (RPC) capability.  This is a script called \verb!xspctrl! found in \verb!/opt/xce/html/svc! and it contains various options.  Particularly, functional calls to this script include the ability to enable and disable for all of the Safeplug settings, including Tor, ad block, and Tor relay.  None of them require any arguments in the POST string.

@@

\subsection{Insider Attack}
Since the Safeplug has no validation or authentication on the settings page or these RPC calls, any malicious party inside the network could easily modify the settings.  Such an adversary with a computer could load the Safeplug's settings page and adjust options such as disabling Tor or adding a site to the whitelist; since this page is meant to be accessible to normal Internet users, anyone can perform this attack.  Unlike many home routers, there is no username/password combination necessary to access this page.

@@

Since the RPC version of the attack just involves basic Internet tools (the ability to send a POST request), the attacker could also be any kind of device on the local network, or the local gateway if it is compromised.  The NSA ``Spymall'' catalog leaked in December shows tools for compromising a number of different devices and home routers are traditionally insecure \cite{spymall}.  It is easy to imagine any malicious party, not just one with the resources of a government (although governments might be some of the most interested parties in attacking a Tor proxy), compromising the gateway and using that access to make a disabling RPC call into the Safeplug.  This would occur silently from the perspective of a client unless they happen to check the settings page for the Safeplug.  Instead, the client would continue browsing with a belief that they are protected by their use of the Tor network, while in fact any external adversary can track their traffic.

@@

The largest observed time to send requests to the 192.168.0.0/24 space was approximately 400 milliseconds; the entire attack costs approximately 800 milliseconds for sending requests to both 192.168.0.0/24 and 192.168.1.0/24 ranges - even when the website was being loaded over Tor.  In the case of a private network in the range of 172.16.0.0/16, the attack took less than 12 minutes (this generates script timeout warnings in most major browsers, which affects the timing of this attack).  This means that it would take a few hours to send requests to the full 172.16.0.0/12 range, which is commonly used in business networks.  The final private network space is 10.0.0.0/8 which is too large for an exhaustive search, but some simple optimization might make it feasible as well.  For example, using a GET request to get and parse the Safeplug settings page would allow the script to positively identify the Safeplug and stop the search.  However, the 192.168.0.0/24 and 192.168.1.0/24 ranges are much more common in home networks; because Safeplug is geared towards home network use, in most cases the script will take less than a second, a trivial amount of time for the attacker to spend.

@@

Having a publically available root password means that SSH can be done effectively without authentication.  We tried the SSH procedure twice, once before the Internet connection and activation, and once afterwards.  Before the activation and update procedure, SSH was not available.  The simple \verb!Hbplug! software on the box could not accept this RPC call.  However, once the box was updated and had Lighttpd installed, the SSH procedure was available and we could download the contents of the root filesystem for analysis.

@@

\section{Discussion}
\subsection{Engineering Fixes}
The most critical engineering fix is authentication in the POST calls to prevent the CSRF attack.  A typical example is a cookie and a hidden form field set in the settings page of the Safeplug hosts; the cookie must be returned by the browser when making the POST request to the RPC server \cite{csrfdef}.  Although someone doing a CSRF attack such as the one described above could get the cookie sent, because of the same-origin policy, the adversary would not be able to examine the contents of the cookie to determine what to put in the form field.

@@

\subsection{Opportunities}
Despite all the structural problems, is there a market for a Torifying piece of hardware?  Given the security pitfalls in comparison to a piece of software such as the Tor Browser Bundle, there seems to be no reason for a user that can run the Tor Browser Bundle to purchase the Safeplug or any other device.  For mobile phones, the proxy problems with mobility contribute to an already high usability cost.  However, there are an emerging class of ``smart home'' devices which may connect to the Internet.  It is possible that some of these devices can be configured to use an HTTP proxy or some other middle box to Torify their traffic to an external service provider.  For them, is the benefit of some anonymity via a Safeplug-like device worthwhile?  Since the data sent by these devices to the service provider likely contains identifying information, the use of Tor probably only protects the user's location at the expense of connection time and load on the Tor network.  Since proxy configuration on such devices is likely to be difficult and the amount of information hidden is unlikely to be worth the effort, a Torifying box that functions as a proxy has questionable use in this space as well.

@@

\bibitem{law} The Legal FAQ for Tor Relay Operators. \url{https://www.torproject.org/eff/tor-legal-faq}.
